Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-17 paper-2023-acsos-pulverization.tex
Fix line number style
pass on III.C

@@

The second \ac{dsl} supports the definition of the mapping between pulverised components and specific hosts,
as well as the definition of reactive reconfiguration policies.
%
It works with the concepts of \texttt{Host}
(associated to \texttt{Capability}),
\texttt{ReconfigurationEvent},
and \texttt{ReconfigurationRule}.
%
Using \Cref{lst:runtime-configuration} as a reference example,
we show how reconfiguration events can be captured at the type system level
by expressing them as a predicate over the asynchronous flow of \texttt{events} the system's state.
%
Similarly, hosts can be configured by defining their name and capabilities.
%
Once the hosts composing the system have been configured,
the entire infrastructure can be set up by defining,
for each logical device,
which host should host each pulverised component.
%
Additionally,
reconfiguration rules can be defined to specify how the system should react to reconfiguration events.
%
In this context, the \ac{dsl} exposes a special syntax to express the migration of a pulverised component on a different host.
%
Crucially, being the DSL internal,
specialised behaviour not supported by the \ac{dsl} can be defined in the host language directly:
configuration blocks surrounded by curly brackets are,
in fact,
plain lambda expressions, supporting any kind of computation.

@@

A \texttt{ReconfigurationEvent} is characterized by the \emph{events}
that it produces and the \emph{condition} that must be satisfied to trigger the reconfiguration.
%
The \emph{events} are represented as an asyncronous stream of valued produced by the device and the
\emph{condition} is a predicate that is evaluated on the stream of events.
%
At the first match of the condition, the reconfiguration is triggered and the system is reconfigured with the new deployment.
%
The~\Cref{lst:reconfiguration-events} shows an example of the definition of a reconfiguration event.

\lstinputlisting[
    float=ht,
    language=Kotlin,
    caption={Example of the definition of a reconfiguration event.},
    label=lst:reconfiguration-events,
]{listings/ReconfigurationEvents.kt}

>>>>

\lstset{xleftmargin=0.3cm,numbersep=5pt}

@@

The second \ac{dsl} supports the definition of the mapping between pulverised components and specific hosts,
as well as the definition of reactive reconfiguration policies.
%
It works with the concepts of \texttt{Host}
(associated to \texttt{Capability}),
\texttt{ReconfigurationEvent},
and \texttt{ReconfigurationRule}.
%
Using \Cref{lst:runtime-configuration} as a reference example,
we show how reconfiguration events can be captured at the type system level
by expressing them as a predicate over an asynchronous flow of \texttt{events} influencing the system's state.
%
Similarly, hosts can be configured by defining their name and capabilities.
%
Once the hosts composing the system have been configured,
the entire infrastructure can be set up by defining,
for each logical device,
which host should host each pulverised component.
%
Additionally,
reconfiguration rules can be defined to specify how the system should react to reconfiguration events.
%
In this context, the \ac{dsl} exposes a special syntax to express the migration of a pulverised component on a different host.
%
Crucially, being the DSL internal,
specialised behaviour not supported by the \ac{dsl} can be defined in the host language directly:
configuration blocks surrounded by curly brackets are,
in fact,
plain lambda expressions, supporting any kind of computation.

@@

% A \texttt{ReconfigurationEvent} is characterized by the \emph{events}
% that it produces and the \emph{condition} that must be satisfied to trigger the reconfiguration.
% %
% The \emph{events} are represented as an asyncronous stream of valued produced by the device and the
% \emph{condition} is a predicate that is evaluated on the stream of events.
% %
% At the first match of the condition, the reconfiguration is triggered and the system is reconfigured with the new deployment.
% %
% The~\Cref{lst:reconfiguration-events} shows an example of the definition of a reconfiguration event.

% \lstinputlisting[
%     float=ht,
%     language=Kotlin,
%     caption={Example of the definition of a reconfiguration event.},
%     label=lst:reconfiguration-events,
% ]{listings/ReconfigurationEvents.kt}
